Structured Versus Decorated Cospans

### 2020-11-25 cospans.tex
Some changes to Section 3

In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting.  Suppose $\A$ is a monoidal category. Then there is a bijection between the following two things:
\begin{itemize}
\item lax monoidal structures on a pseudofunctor $F\maps\A\to\Cat$
\item monoidal structures on $\inta F$ such that $U \maps \inta F \to \A$ is strict monoidal and the tensor product in $\inta F$ preserves cocartesian liftings.  
\end{itemize}
We call the former \define{monoidal opindexed categories}, and the latter \define{monoidal opfibrations}. If the monoidal structure of $\A$ is cocartesian, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.  These correspondences can be enhanced to 2-equivalences:
%-In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a monoidal category $\A$ there is a bijection between \define{monoidal opindexed categories}, which are lax monoidal pseudofunctors $F\maps\A\to\Cat$, and \define{monoidal opfibrations}, which are opfibrations $U \maps \X \to \A$ where $\X$ is monoidal, $U$ is strict monoidal, and $\otimes_\X$ preserves cocartesian liftings.   This bijection sends a monoidal opindexed category $F \maps \A \to \Cat$ to its Grothendieck construction $U \maps \inta F \to \A$.  If the monoidal structure on $\A$ is in fact cocartesian, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.   Further, all these correspondences lift to 2-equivalences:
{\chris There is a commented out passage of your earlier take here. I think I preferred your earlier more discussional version. Now having the two bullets above almost totally coincides with the three lines with arrows between them in the sketch of proof below. Feels like saying the same thing twice, whereas earlier you were really just giving brief definitions before diving in the theorem.}

@@

\begin{proof}
This was shown by Moeller and the third author \cite[Theorems~3.13\&4.1]{MV}. In summary, for a cocartesian base we have correspondences
\begin{gather}
\textrm{lax monoidal pseudofunctors }F\maps(\A,+)\to(\Cat,\times) \notag\\
\Updownarrow \notag\\
\textrm{monoidal opfibrations }U\maps(\X,\otimes)\to(\A,+) \notag\\
\Updownarrow \notag\\
\textrm{pseudofunctors } \tilde{F} \maps \A\to\bicat{MonCat} \notag
\end{gather}
The second equivalence was also earlier observed by Shulman \cite{Shulman2008}.

@@

We have now laid all the necessary background to formally construct an isomorphism between the double category of decorated cospans and the double category of structured cospans, with starting point a symmetric lax monoidal pseudofunctor into $\Cat$.

>>>>

In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a monoidal category $\A$ there is a bijection between \define{monoidal opindexed categories}, which are lax monoidal pseudofunctors $F\maps\A\to\Cat$, and \define{monoidal opfibrations}, which are opfibrations $U \maps \X \to \A$ where $\X$ is monoidal, $U$ is strict monoidal, and $\otimes_\X$ preserves cocartesian liftings.   This bijection sends a monoidal opindexed category $F \maps \A \to \Cat$ to its Grothendieck construction $U \maps \inta F \to \A$.  If the monoidal structure on $\A$ is in fact cocartesian, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps\A\to\bicat{MonCat}$ where $\bicat{MonCat}$ is 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.   Further, all these correspondences lift to 2-equivalences:
%{\chris There is a commented out passage of your earlier take here. I think I preferred your earlier more discussional version. Now having the two bullets above almost totally coincides with the three lines with arrows between them in the sketch of proof below. Feels like saying the same thing twice, whereas earlier you were really just giving brief definitions before diving in the theorem.}

@@

\begin{proof}
This was shown by Moeller and the third author \cite[Theorems~3.13\&4.1]{MV}. In summary, for a cocartesian base $\A$ we have correspondences
\begin{gather}
\textrm{lax monoidal pseudofunctors }F\maps(\A,+)\to(\Cat,\times) \notag\\
\Updownarrow \notag\\
\textrm{monoidal opfibrations }U\maps(\X,\otimes)\to(\A,+) \notag\\
\Updownarrow \notag\\
\textrm{pseudofunctors } \tilde{F} \maps \A\to\bicat{MonCat} \notag
\end{gather}
The second equivalence was also earlier observed by Shulman \cite{Shulman2008}.

@@

We have now have all the necessary background to formally construct an isomorphism between the double category of decorated cospans and the double category of structured cospans, starting from a symmetric lax monoidal pseudofunctor $F \maps (\A, +) \to (\Cat, \times)$ that factors through $\Rex$ as a pseudofunctor.
